Autonomous Oceanographic Data Collection. Learning Excursion Sets of Vector-valued Gaussian Random Fields \\or\\ Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-06-27 main_new.tex
Updates from Overleaf

\begin{equation*}
\begin{split}
\currentEEMV(\bm{x})
&=\int_{\domain^2} 
\varPhi_{2\no}
\left(
(\bt, \bt); ~ \mu((u,v)), 
K((u,v),(u,v))
\right) 
\
\mathrm{d}\mes^{\otimes} %\mes 
%\productMeasure 
(u,v)\\
&-\int_{\domain^2} \varPhi_{2\no}
\left(
\left(
\begin{matrix}
\bt-\currentMean{\uu}\\
\bt-\currentMean{\vv}
\end{matrix}
\right);~
\mathbf{\tilde{\Sigma}}_{[\stage]}(\uu, \vv)
\right)
\mathrm{d}\mes^{\otimes} %\mes 
%\productMeasure 
(u,v)
\end{split}
\end{equation*}
where the matrix $\mathbf{\tilde{\Sigma}}_{[n]}(\uu, \vv)$ is defined blockwise as
\begin{equation*}
\begin{split}
\mathbf{\tilde{\Sigma}}_{[n]}(\uu, \vv)&=
\left(
\begin{matrix}
\tilde{\Sigma}_{1,1}(\uu, \uu) & \tilde{\Sigma}_{1,2}(\uu, \vv)\\
\tilde{\Sigma}_{2,1}(\vv, \uu) & \tilde{\Sigma}_{2,2}(\vv, \vv)
\end{matrix}\right)
\end{split}
\end{equation*}
with blocks given by
\begin{equation*}
\begin{split}
\tilde{\Sigma}_{i,j}(u, v) &= \lambda_{[n+1,n+1]}(\uu)^T k_{[n]}(\bm{x},\bm{x}) \lambda_{[n+1,n+1]}(\vv) + \delta_{i,j}\futureCov{\uu, \vv}
\end{split}
\end{equation*}
and the other blocks are defined by following the same logic, exchanging the role of $\uu$ and $\vv$.
\end{propo}

@@

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary
affiliation in an early version of this work.  The authors would also
like to thank Niklas Linde of the University of Lausanne for providing
constructive feedback on a version of the manuscript.

>>>>

\begin{equation*}
\begin{split}
\currentEEMV(\bm{x})
&=\int_{\domain^2} 
\varPhi_{2\no}
\left(
(\bt, \bt); ~ \mu((u,v)), 
K((u,v),(u,v))
\right) 
\
\mathrm{d}\mes^{\otimes} %\mes 
%\productMeasure 
(u,v)\\
&-\int_{\domain^2} \varPhi_{2\no}
\left(
\left(
\begin{matrix}
\bt-\currentMean{\uu}\\
\bt-\currentMean{\vv}
\end{matrix}
\right);~
\mathbf{\tilde{\Sigma}}_{[\stage]}(\uu, \vv)
\right)
\mathrm{d}\mes^{\otimes} %\mes 
%\productMeasure 
(u,v)
\end{split}
\end{equation*}
where the matrix $\mathbf{\tilde{\Sigma}}_{[n]}(\uu, \vv)$ is defined blockwise as
\begin{equation*}
\begin{split}
\mathbf{\tilde{\Sigma}}_{[n]}(\uu, \vv)&=
\left(
\begin{matrix}
\tilde{\Sigma}_{1,1}(\uu, \uu) & \tilde{\Sigma}_{1,2}(\uu, \vv)\\
\tilde{\Sigma}_{2,1}(\vv, \uu) & \tilde{\Sigma}_{2,2}(\vv, \vv)
\end{matrix}\right)
\end{split}
\end{equation*}
with blocks given, for $i,j\in \{1,2\}$ and $u,v\in \domain$, by
\begin{equation*}
\begin{split}
\tilde{\Sigma}_{i,j}(u, v) &= \lambda_{[n+1,n+1]}(\uu)^T k_{[n]}(\bm{x},\bm{x}) \lambda_{[n+1,n+1]}(\vv) + \delta_{i,j}\futureCov{\uu, \vv}.
\end{split}
\end{equation*}
%and the other blocks are defined by following the same logic, exchanging the role of $\uu$ and $\vv$.
\end{propo}

@@

TOF acknowledges support from the Centre for Autonomous Marine
Operations and Systems (AMOS), Center of Excellence, project number
223254, and the Applied Underwater Robotics Labortatory (AURLab). CT
and DG acknowledge support from the Swiss National Science Foundation,
project number 178858. JE and KR acknowledge support from Norwegian
research council (RCN), project number 305445. DG would like to
aknowledge support of Idiap Research Institute, his primary affiliation in an early version of this manuscript.  The authors would also
like to thank Niklas Linde of the University of Lausanne for providing constructive feedback on this work.
